### 2022-08-11 draft.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@481219c9ee03a62380abfc0b350bf453c57f21b2 🚀

Understanding the ecological constraints that shape species interactions
networks and predicting their emerging structure are thus two
complementary aims of network ecology. This distinction between
understanding and predicting is essential when using statistical and
mathematical models in network ecology and interpreting them. On one
hand, null models help us identify potential ecological mechanisms that
drive species interactions and constrain ecological networks. Null
models generate a distribution for a target measure using a set of rules
that exclude the mechanism of interest (Fortuna and Bascompte 2006;
Delmas et al. 2019). The difference between the model and empirical data
helps us evaluate the effect of this ecological process in nature. On
the other hand, predictive models can help fill many gaps on species
interactions data. A variety of such models have recently been developed
using machine learning and other statistical tools, most of which are
presented in Strydom et al. (2021). However, given the constrained
nature of ecological networks, it is surprising that the principle of
maximum entropy, a rigorous mathematical method designed for both the
analysis and prediction of constrained systems, has been barely used in
network ecology.

@@

We tested our analytical and heuristic MaxEnt models against open
food-web data queried from three different sources and integrated into
what we call our \emph{complete dataset}. These sources include (1)
terrestrial and aquatic food webs sampled globally and archived on the
ecological interactions database Mangal; (2) freshwater stream food webs
from New Zealand; and (3) aquatic food webs from Tuesday Lake (Michigan,
United States). First, all food webs archived on \texttt{mangal.io}
(Timothee Poisot et al. 2016; Banville, Vissault, and Poisot 2021) were
directly queried from the database (\(N = 235\)). Most ecological
networks archived on Mangal are multilayer networks, i.e.~networks that
describe different types of interactions. We kept all networks whose
interactions were mainly of predation and herbivory types, and removed
the largest network (\(S = 714\)) for computational efficiency reasons.
Then, to this set we added food webs from two different sources: the
New-Zealand dataset (\(N = 21\); Pomeranz et al. 2018) and the Tuesday
Lake dataset (\(N = 2\); Cohen, Jonsson, and Carpenter 2003). Our
complete dataset thus contained a total of \(257\) food webs. Of the
New-Zealand and Tuesday Lake datasets, \(19\) networks had data on
species' relative abundances that were used in the neutral model (Box
2). These \(19\) food webs constitute our \emph{abundance dataset},
which is a subset of our complete dataset.

@@

@@

The joint degree distribution \(p(k_{in},k_{out})\) is a joint discrete
probability distribution describing the probability that a species has
\(k_{in}\) predators and \(k_{out}\) preys, with \(k_{in}\) and
\(k_{out}\) \(\epsilon\) \([0, S]\). Basal species (e.g., plants) have a
\(k_{out}\) of \(0\), whereas top predators have a \(k_{in}\) of \(0\).
In contrast, the maximum number of preys and predators a species can
have is set by the number of species \(S\) in the food web. Here we show
how the joint degree distribution of maximum entropy can be obtained
given knowledge of \(S\) and \(L\).

@@

The first constraint \(g_1\) is our normalizing constraint, whereas the
other two (\(g_2\) and \(g_3\)) fix the average of the marginal
distributions of \(k_{in}\) and \(k_{out}\) to the linkage density
\(L/S\). It is important to notice that
\(\langle k_{in} \rangle = \langle k_{out} \rangle\) because every edge
is associated to a predator and a prey. Therefore, without any further
constraints, we expect the joint degree distribution of maximum entropy
to be a symmetric probability distribution with regards to \(k_{in}\)
and \(k_{out}\). However, this does not mean that the joint degree
\emph{sequence} will be symmetric, since the joint degree sequence is
essentially a random realization of its probabilistic counterpart.

@@

where \(\lambda_1\), \(\lambda_2\), and \(\lambda_3\) are the Lagrange
multipliers. The probability distribution that maximizes entropy is
obtained by finding these values. As pointed out in the introduction,
\(F\) is just Shannon's entropy to which we added terms that each sums
to zero (our constraints). \(F\) is maximized by setting to 0 its
partial derivative with respect to \(p(k_{in},k_{out})\). Because the
derivative of a constant is zero, this gives us:

@@

We predicted the joint degree distribution of maximum entropy for each
food web in our complete dataset, i.e.~using their numbers of species
and numbers of interactions as state variables. We then sampled one
realization of the degree sequence for each network using the
probabilities given by the joint degree distribution. In
fig.~\ref{fig:joint_dd} (left panels), we show the relationship between
\(k_{out}\) and \(k_{in}\) standardized by the number of species in
their networks, for empirical and maximum entropy joint degree
distributions. We see that our model predicts higher values of
generality and vulnerability compared to empirical food webs
(i.e.~relative values of \(k_{out}\) and \(k_{in}\) closer to \(1\)).
However, plotting the difference between predicted and empirical values
for each species gives a different perspective. The right panel of
fig.~\ref{fig:joint_dd} presents these differences when species are
ordered by their total degree in their network (i.e.~by the sum of their
in and out-degrees). Indeed, our predicted joint degree sequences have
the same number of species as their empirical counterparts, but they are
species agnostic; in other words, instead of predicting a value for each
species directly, we predicted the entire joint degree sequence without
taking into account species' identity. The challenge is to associate
predictions with empirical data. If we associate each node according to
their rank in total degrees, we see that species predicted to be have a
higher generality (number of preys) generally have a lower vulnerability
(number of preys) than what is observed (and conversely). This is
because the difference in total degree (\(k_{out} + k_{in}\)) is
minimized when species are ordered by their total degrees in both
predicted and empirical sets (i.e.~the average sum of relative
\(k_{out}\) and \(k_{in}\) is close to \(0\) across all species). This
result shows that the differences between predicted and empirical
degrees (in and out) are low for most species when ordered by their
total degrees and that there is no apparent biases towards in or out
degrees. In fig.~S1, we show how these differences change when species
are instead ordered by their out-degrees (left panel) and in-degrees
(right panel), respectively.

\begin{figure}
\hypertarget{fig:joint_dd}{%
\centering
\includegraphics{figures/joint_degree_dist.png}
\caption{Relative number of predators (\(k_{in}\)) as a function of the
relative number of preys (\(k_{out}\)) for each species in (a) empirical
and (b) maximum entropy joint degree sequences. Empirical networks
include all food webs archived on Mangal, as well as the New-Zealand and
Tuesday Lake datasets (our complete dataset). The predicted joint degree
sequences were obtained after sampling one realization of the joint
degree distribution of maximum entropy for each network. (c) Difference
between predicted and empirical values when species are ordered
according to their total degrees. In all panels, each dot corresponds to
a single species in one of the network of our complete
dataset.}\label{fig:joint_dd}
}
\end{figure}

We can describe the shape of the joint degree distribution by comparing
its marginal distributions with one another. Doing so allows us to
evaluate how much the shape of the joint degree distribution of maximum
entropy differs from empirical data. We plotted the Kullback--Leibler
(KL) divergence between in and out-degree sequences to compare the
symmetry of empirical and maximum entropy joint degree sequences
fig.~\ref{fig:kl_diverg}. As we expected, our model predicted more
similar in-degree and out-degree distributions than empirical data
(shown by a lower KL divergence). However, this difference decreased
with connectance right panel of \ref{fig:kl_diverg}. This suggests that
other ecological constraints might be needed to account for the
asymmetry of the joint degree distribution, especially for networks with
a lower connectance. This might be due to the fact that food webs with
low connectance are typically harder to predict than food webs with high
connectance. Indeed, in low connectance systems, what makes two species
interact might be more important for predictions than in high
connectance systems, in which what prevents species from interacting
might be more meaningful. This implies that more ecological information
might be needed in food webs with fewer numbers of interactions because
more nuances determine interactions compared to non-interactions.

\begin{figure}
\hypertarget{fig:kl_diverg}{%
\centering
\includegraphics{figures/kl_divergence.png}
\caption{(a) Probability density of KL divergence between in and
out-degree sequences of empirical and maximum entropy joint degree
sequences. (b) Difference between the KL divergence of empirical and
predicted networks as a function of connectance. In both panels,
empirical networks include all food webs archived on Mangal, as well as
the New-Zealand and Tuesday Lake datasets (our complete dataset). The
joint degree sequence of simulated networks was obtained after sampling
one realization of the joint degree distribution of maximum entropy for
each network.}\label{fig:kl_diverg}
}
\end{figure}

@@

\hypertarget{tbl:measures_all}{}
\begin{longtable}[]{@{}rrrrrrrr@{}}
\caption{\label{tbl:measures_all}Standardized mean differences of
predicted network measures with empirical data for all networks
(\(n = 257\)). Positive (negative) values indicate that the measure is
overestimated (underestimated) on average. Empirical networks are all
food webs archived on Mangal, as well as the New Zealand and Tuesday
Lake food webs (our complete dataset). Null 1: Type I null model based
on connectance. MaxEnt 1: Type I MaxEnt network model based on
connectance. Null 2: Type II null model based on the joint degree
sequence. MaxEnt 2: Type II MaxEnt network model based on the joint
degree sequence. \(\rho\): nestedness measured by the spectral radius of
the adjacency matrix. \emph{maxtl}: maximum trophic level. \emph{diam}:
network diameter. \emph{MxSim}: average maximum similarity between
species pairs. \emph{Cannib}: proportion of cannibal species (self
loops). \emph{Omniv}: proportion of omnivorous species. \emph{entropy}:
SVD entropy.}\tabularnewline
\toprule
model & rho & maxtl & diam & MxSim & Cannib & Omniv &
entropy\tabularnewline
\midrule
\endfirsthead
\toprule
model & rho & maxtl & diam & MxSim & Cannib & Omniv &
entropy\tabularnewline
\midrule
\endhead
null 1 & -0.167 & 0.980 & 1.428 & -0.502 & 2.007 & 1.493 &
0.056\tabularnewline
MaxEnt 1 & -0.226 & 0.831 & 1.274 & -0.524 & 1.982 & 1.863 &
0.106\tabularnewline
null 2 & 0.160 & -0.125 & 0.016 & 0.007 & 1.078 & 0.559 &
-0.023\tabularnewline
MaxEnt 2 & -0.015 & 0.178 & 0.565 & -0.282 & 0.698 & 0.589 &
0.058\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{figure}
\hypertarget{fig:motifs}{%
\centering
\includegraphics{figures/motifs_distribution.png}
\caption{Motifs profile of empirical, maximum entropy, and null food
webs. Empirical networks include all food webs archived on Mangal, as
well as the New-Zealand and Tuesday Lake datasets (our complete
dataset). Maximum entropy networks were estimated using a simulated
annealing algorithm to find the network of maximum SVD entropy while
maintaining the connectance (type I MaxEnt network model) or the joint
degree sequence (type II MaxEnt network model). The predictions of the
types I and II null models are also plotted. Boxplots display the median
proportions of each motif (middle horizontal lines), as well as the
first (bottom horizontal lines) and third (top horizontal lines)
quartiles. Vertical lines encompass all data points that fall within
\(1.5\) times the interquartile range from both quartiles, and dots are
data points that fall outside this range. Motifs names are from Stouffer
et al. (2007).}\label{fig:motifs}
}
\end{figure}

\begin{figure}
\hypertarget{fig:motifs_rel}{%
\centering
\includegraphics{figures/motifs_relations.png}
\caption{Relationship between motifs proportions of empirical, maximum
entropy, and null food webs. Empirical networks include all food webs
archived on Mangal, as well as the New-Zealand and Tuesday Lake datasets
(our complete dataset). Maximum entropy networks were estimated using a
simulated annealing algorithm to find the network of maximum SVD entropy
while maintaining the connectance (type I MaxEnt network model) or the
joint degree sequence (type II MaxEnt network model). The predictions of
the types I and II null models are also plotted. Regression lines are
plotted in each panel. Motifs names are from Stouffer et al.
(2007).}\label{fig:motifs_rel}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:measures}{%
\centering
\includegraphics{figures/measures_emp_maxent.png}
\caption{Relationship between the structure of empirical and maximum
entropy food webs. Empirical networks include all food webs archived on
Mangal, as well as the New-Zealand and Tuesday Lake datasets (our
complete dataset). Maximum entropy networks were estimated using a
simulated annealing algorithm to find the network of maximum SVD entropy
while maintaining the joint degree sequence (type II MaxEnt network
model). (a) Nestedness (estimated using the spectral radius of the
adjacency matrix), (b) the maximum trophic level, (c) the network
diameter, and (d) the SVD entropy were measured on these empirical and
maximum entropy food webs. The identity line is plotted in each
panel.}\label{fig:measures}
}
\end{figure}

@@

>>>>

Understanding the ecological constraints that shape species interactions
networks and predicting their emerging structure are thus two
complementary aims of network ecology. This distinction between
understanding and predicting is essential when using statistical and
mathematical models in network ecology and interpreting them. On one
hand, null models help us identify potential ecological mechanisms that
drive species interactions and constrain ecological networks. Null
models generate a distribution for a target measure using a set of rules
that exclude the mechanism of interest (Fortuna and Bascompte 2006;
Delmas et al. 2019). The deviation between the model and empirical data
helps us evaluate the effect of this ecological process in nature. On
the other hand, predictive models can help fill many gaps on species
interactions data. A variety of such models have recently been developed
using machine learning and other statistical tools, most of which are
presented in Strydom et al. (2021). However, given the constrained
nature of ecological networks, it is surprising that the principle of
maximum entropy, a rigorous mathematical method designed for both the
analysis and prediction of constrained systems, has been barely used in
network ecology.

@@

We tested our analytical and heuristic MaxEnt models against open
food-web data queried from three different sources and integrated into
what we call our \emph{complete dataset}. These sources include (1)
terrestrial and aquatic food webs sampled globally and archived on the
ecological interactions database Mangal; (2) freshwater stream food webs
from New Zealand; and (3) aquatic food webs from Tuesday Lake (Michigan,
United States). First, all food webs archived on \texttt{mangal.io}
(Timothee Poisot et al. 2016; Banville, Vissault, and Poisot 2021) were
directly queried from the database (\(N = 235\)). Most ecological
networks archived on Mangal are multilayer networks, i.e.~networks that
describe different types of interactions. We kept all networks whose
interactions were mainly of predation and herbivory types, and removed
the largest network (\(S = 714\)) for computational efficiency reasons.
Then, to this set we added food webs from two different sources: the New
Zealand dataset (\(N = 21\); Pomeranz et al. 2018) and the Tuesday Lake
dataset (\(N = 2\); Cohen, Jonsson, and Carpenter 2003). Our complete
dataset thus contained a total of \(257\) food webs. Of the New Zealand
and Tuesday Lake datasets, \(19\) networks had data on species' relative
abundances that were used in the neutral model (Box 2). These \(19\)
food webs constitute our \emph{abundance dataset}, which is a subset of
our complete dataset.

@@

Our analytical approach is the most common way to use and develop
maximum entropy models. As shown above, starting from a defined set of
constraints, a mathematical expression for the target distribution is
derived using the method of Lagrange multipliers. The derived
distribution of maximum entropy is unique and least biased given the
constraints used. Although we refer to this approach as analytic,
finding the values of the Lagrange multipliers usually requires the use
of numerical methods. Here we use MaxEnt to derive two species level
properties in food webs: the joint degree distribution and the degree
distribution. The degree distribution has driven the attention of
ecologists because of its role in determining the assembly of ecological
networks (Vázquez 2005), shaping their emerging structure (Fortuna et
al. 2010), and understanding interaction mechanisms (Williams 2011). As
noted above, although the degree distribution of maximum entropy has
already been derived in bipartite networks (Williams 2011), we show in
much greater details its mathematical derivation in food webs. But
first, we derive the joint degree distribution, a related property that
holds significantly more ecological information than the degree
distribution.

@@

The joint degree distribution \(p(k_{in},k_{out})\) of a food web with
\(S\) species is a joint discrete probability distribution describing
the probability that a species has \(k_{in}\) predators and \(k_{out}\)
preys, with \(k_{in}\) and \(k_{out}\) \(\epsilon\) \([0, S]\). Basal
species (e.g., plants) have a \(k_{out}\) of \(0\), whereas top
predators have a \(k_{in}\) of \(0\). In contrast, the maximum number of
preys and predators a species can have is set by the number of species
in the food web. Here we show how the joint degree distribution of
maximum entropy can be obtained given knowledge of the number of species
\(S\) and the number of interactions \(L\).

@@

The first constraint \(g_1\) is our normalizing constraint, whereas the
other two (\(g_2\) and \(g_3\)) fix the average of the marginal
distributions of \(k_{in}\) and \(k_{out}\) to the linkage density
\(L/S\). It is important to notice that
\(\langle k_{in} \rangle = \langle k_{out} \rangle\) because every edge
is associated to a predator and a prey. Therefore, without using any
further constraints, we would expect the joint degree distribution of
maximum entropy to be a symmetric probability distribution with regards
to \(k_{in}\) and \(k_{out}\). However, this does not mean that the
joint degree \emph{sequence} will be symmetric, since the joint degree
sequence is essentially a random realization of its probabilistic
counterpart.

@@

where \(\lambda_1\), \(\lambda_2\), and \(\lambda_3\) are the Lagrange
multipliers. The probability distribution that maximizes entropy is
obtained by finding these values. As pointed out above, \(F\) is just
Shannon's entropy to which we added terms that each sums to zero (our
constraints). \(F\) is maximized by setting to 0 its partial derivative
with respect to \(p(k_{in},k_{out})\). Because the derivative of a
constant is zero, this gives us:

@@

We assessed the empirical support of this expression using all food webs
in our complete dataset. First, we predicted the joint degree
distribution of maximum entropy for each of these food webs, i.e.~using
their number of species and number of interactions as state variables.
Then, we sampled one realization of the joint degree sequence for each
network using the probabilities given by the joint degree distribution
of maximum entropy, while fixing the total number of interactions. This
gave us a random realization of the number of prey and predators for
each species in each network. We standardized the predicted \(k_{out}\)
and \(k_{in}\) of each species by the total number of species in their
network to generate relative values, which can be compared across
networks. In fig.~\ref{fig:joint_dd} (left panels), we show the
relationship between these relative \(k_{out}\) and \(k_{in}\) obtained
from the joint degree distributions of maximum entropy (bottom panel)
and this relationship using empirical values (top panel). We observe
that our model predicts higher values of generality and vulnerability
compared to empirical food webs (i.e.~relative values of \(k_{out}\) and
\(k_{in}\) both closer to \(1\)) for many species. In other words, our
model predicts that species that have many predators also have more prey
than what is observed empirically (and conversely). This is not
surprising, given that our model did not include biological factors
preventing generalist predators from having many prey. Nevertheless,
with the exception of these generalist species, MaxEnt adequately
predicts that most species have low generality and vulnerability values.

Examining the difference between predicted and empirical values for each
species gives a slightly different perspective (right panel of
fig.~\ref{fig:joint_dd}). To do so, we must first associate each of our
predictions to a specific species in a network in order to make that
comparison. Indeed, our predicted joint degree sequences have the same
number of species (elements) as their empirical counterparts, but they
are species agnostic. In other words, instead of predicting a value for
each species directly, we predicted the entire joint degree sequence
without taking into account species' identity. The challenge is thus to
adequately associate predictions with empirical data. In
fig.~\ref{fig:joint_dd}, we present these differences when species are
ordered by their total degree in their respective networks (i.e.~by the
sum of their in and out-degrees). This means that the species with the
highest total degree in its network will be associated with the highest
prediction, and so forth. Doing so, we see that species predicted to
have a higher number of predators than what is observed generally have a
lower number of prey than what is observed (and conversely). This is
because the difference in total degree (\(k_{out} + k_{in}\)) between
predictions and empirical data is minimized when species are ranked by
their total degree (i.e.~the average deviation of the sum of relative
\(k_{out}\) and \(k_{in}\) is close to \(0\) across all species). This
result thus shows that the difference between predicted and empirical
total degrees is low for most species when ordered by their total
degrees. There are no apparent biases towards in or out degrees. In
fig.~S1, we show how these differences change when species are instead
ordered by their out-degrees (left panel) and in-degrees (right panel),
respectively.

\begin{figure}
\hypertarget{fig:joint_dd}{%
\centering
\includegraphics{figures/joint_degree_dist.png}
\caption{Relative number of predators (\(k_{in}\)) as a function of
their relative number of prey (\(k_{out}\)) for each species in (a)
empirical and (b) joint degree sequences obtained from the analytical
MaxEnt model. Empirical networks include most food webs archived on
Mangal, as well as the New Zealand and Tuesday Lake datasets (our
complete dataset). The predicted joint degree sequences were obtained
after sampling one realization of the joint degree distribution of
maximum entropy for each network, while keeping the total number of
interactions constant. (c) Difference between predicted and empirical
values when species are ordered according to their total degrees. In
each panel, each dot corresponds to a single species in one of the
networks.}\label{fig:joint_dd}
}
\end{figure}

Another way to evaluate the empirical support of the predicted joint
degree sequences is to compare their shape with the ones of empirical
food webs. We can describe the shape of a joint degree sequence by
comparing its marginal distributions with one another. To do so, we
calculated the Kullback--Leibler (KL) divergence between the in and
out-degree sequences sampled from the joint degree distribution of
maximum entropy. Similarly, we calculated the divergence between the in
and out-degree sequences obtained empirically. This allows us to compare
the symmetry of empirical and predicted joint degree sequences (left
panel of fig.~\ref{fig:kl_diverg}). As we expected, our model predicts
more similar in-degree and out-degree sequences than empirical data
(shown by lower KL divergence values). However, this difference
decreases with connectance (right panel of fig.~\ref{fig:kl_diverg}).
This might be due to the fact that food webs with a low connectance are
harder to predict than food webs with a high connectance. Indeed, in low
connectance systems, what makes two species interact might be more
important for prediction than in high connectance systems, in which what
prevents species from interacting might be more meaningful. This implies
that more ecological information might be needed in food webs with a low
connectance because more ecological processes determine interactions
compared to non-interactions. Therefore, other ecological constraints
might be needed to account for the asymmetry of the joint degree
distribution, especially for networks with a lower connectance. However,
our MaxEnt model was able to capture quite well the shape of the joint
degree sequence for networks having a high connectance.

\begin{figure}
\hypertarget{fig:kl_diverg}{%
\centering
\includegraphics{figures/kl_divergence.png}
\caption{(a) Probability density of KL divergence between in and
out-degree sequences of empirical and predicted joint degree sequences.
(b) Difference between the KL divergence of empirical and predicted
joint degree sequences as a function of connectance. In both panels,
empirical networks include most food webs archived on Mangal, as well as
the New Zealand and Tuesday Lake datasets (our complete dataset). The
predicted joint degree sequences were obtained after sampling one
realization of the joint degree distribution of maximum entropy for each
network, while keeping the total number of interactions
constant.}\label{fig:kl_diverg}
}
\end{figure}

@@

\hypertarget{tbl:measures_all}{}
\begin{longtable}[]{@{}rrrrrrrr@{}}
\caption{\label{tbl:measures_all}Standardized mean differences of
predicted network measures with empirical data for all networks
(\(n = 257\)). Positive (negative) values indicate that the measure is
overestimated (underestimated) on average. Empirical networks are most
food webs archived on Mangal, as well as the New Zealand and Tuesday
Lake food webs (our complete dataset). Null 1: Type I null model based
on connectance. MaxEnt 1: Type I MaxEnt network model based on
connectance. Null 2: Type II null model based on the joint degree
sequence. MaxEnt 2: Type II MaxEnt network model based on the joint
degree sequence. \(\rho\): nestedness measured by the spectral radius of
the adjacency matrix. \emph{maxtl}: maximum trophic level. \emph{diam}:
network diameter. \emph{MxSim}: average maximum similarity between
species pairs. \emph{Cannib}: proportion of cannibal species (self
loops). \emph{Omniv}: proportion of omnivorous species. \emph{entropy}:
SVD entropy.}\tabularnewline
\toprule
model & rho & maxtl & diam & MxSim & Cannib & Omniv &
entropy\tabularnewline
\midrule
\endfirsthead
\toprule
model & rho & maxtl & diam & MxSim & Cannib & Omniv &
entropy\tabularnewline
\midrule
\endhead
null 1 & -0.167 & 0.980 & 1.428 & -0.502 & 2.007 & 1.493 &
0.056\tabularnewline
MaxEnt 1 & -0.226 & 0.831 & 1.274 & -0.524 & 1.982 & 1.863 &
0.106\tabularnewline
null 2 & 0.160 & -0.125 & 0.016 & 0.007 & 1.078 & 0.559 &
-0.023\tabularnewline
MaxEnt 2 & -0.015 & 0.178 & 0.565 & -0.282 & 0.698 & 0.589 &
0.058\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{figure}
\hypertarget{fig:motifs}{%
\centering
\includegraphics{figures/motifs_distribution.png}
\caption{Motifs profile of empirical, maximum entropy, and null food
webs. Empirical networks include most food webs archived on Mangal, as
well as the New Zealand and Tuesday Lake datasets (our complete
dataset). Maximum entropy networks were estimated using a simulated
annealing algorithm to find the network of maximum SVD entropy while
maintaining the connectance (type I MaxEnt network model) or the joint
degree sequence (type II MaxEnt network model). The predictions of the
types I and II null models are also plotted. Boxplots display the median
proportions of each motif (middle horizontal lines), as well as the
first (bottom horizontal lines) and third (top horizontal lines)
quartiles. Vertical lines encompass all data points that fall within
\(1.5\) times the interquartile range from both quartiles, and dots are
data points that fall outside this range. Motifs names are from Stouffer
et al. (2007).}\label{fig:motifs}
}
\end{figure}

\begin{figure}
\hypertarget{fig:motifs_rel}{%
\centering
\includegraphics{figures/motifs_relations.png}
\caption{Relationship between motifs proportions of empirical, maximum
entropy, and null food webs. Empirical networks include most food webs
archived on Mangal, as well as the New Zealand and Tuesday Lake datasets
(our complete dataset). Maximum entropy networks were estimated using a
simulated annealing algorithm to find the network of maximum SVD entropy
while maintaining the connectance (type I MaxEnt network model) or the
joint degree sequence (type II MaxEnt network model). The predictions of
the types I and II null models are also plotted. Regression lines are
plotted in each panel. Motifs names are from Stouffer et al.
(2007).}\label{fig:motifs_rel}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:measures}{%
\centering
\includegraphics{figures/measures_emp_maxent.png}
\caption{Relationship between the structure of empirical and maximum
entropy food webs. Empirical networks include most food webs archived on
Mangal, as well as the New Zealand and Tuesday Lake datasets (our
complete dataset). Maximum entropy networks were estimated using a
simulated annealing algorithm to find the network of maximum SVD entropy
while maintaining the joint degree sequence (type II MaxEnt network
model). (a) Nestedness (estimated using the spectral radius of the
adjacency matrix), (b) the maximum trophic level, (c) the network
diameter, and (d) the SVD entropy were measured on these empirical and
maximum entropy food webs. The identity line is plotted in each
panel.}\label{fig:measures}
}
\end{figure}

@@

\leavevmode\hypertarget{ref-Vazquez2005DegDisa}{}%
Vázquez, Diego P. 2005. {``Degree Distribution in Plantanimal
Mutualistic Networks: Forbidden Links or Random Interactions?''}
\emph{Oikos} 108 (2): 421--26.
\url{https://doi.org/10.1111/j.0030-1299.2005.13619.x}.

### 2022-08-11 suppmat.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@481219c9ee03a62380abfc0b350bf453c57f21b2 🚀

\begin{figure}
\hypertarget{fig:kin_kout_diff}{%
\centering
\includegraphics{figures/kin_kout_difference.png}
\caption{Difference between predicted and empirical values for the
number of predators \(k_{in}\) and the number of preys \(k_{out}\) when
species are ordered according to (a) their out-degree and (b) their
in-degree. Empirical networks include all food webs archived on Mangal,
as well as the New-Zealand and Tuesday lake datasets (our complete
dataset). The joint degree sequences for simulated networks were
obtained after sampling one realization of the joint degree distribution
of maximum entropy for each network. Each dot corresponds to a single
species in one of the network of our dataset.}\label{fig:kin_kout_diff}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:entropy_dist}{%
\centering
\includegraphics{figures/entropy_distribution.png}
\caption{(a) Distribution of the SVD entropy of MaxEnt food webs (type
II MaxEnt network model) and of empirical food webs. Empirical networks
include all food webs archived on Mangal, as well as the New Zealand and
Tuesday lake datasets (our complete dataset). Maximum entropy networks
were derived using a simulating annealing algorithm to find the network
of maximum SVD entropy while maintaining the joint degree sequence. (b)
Distribution of z-scores of the SVD entropy of all empirical food webs.
Z-scores were computed using the mean and standard deviation of the
distribution of SVD entropy of MaxEnt food webs (type II MaxEnt network
model). The dash line corresponds to the median
z-score.}\label{fig:entropy_dist}
}
\end{figure}

\begin{figure}
\hypertarget{fig:entropy_size}{%
\centering
\includegraphics{figures/difference_entropy.png}
\caption{Difference in SVD entropy between MaxEnt (type II MaxEnt
network model) and empirical food webs as a function of (a) species
richness, (b) the number of links, and (c) connectance. Empirical
networks include all food webs archived on Mangal, as well as the New
Zealand and Tuesday lake datasets (our complete dataset). Maximum
entropy networks were derived using a simulating annealing algorithm to
find the network of maximum SVD entropy while maintaining the joint
degree sequence. Regression lines are plotted in each
panel.}\label{fig:entropy_size}
}
\end{figure}

\begin{figure}
\hypertarget{fig:measures_richness}{%
\centering
\includegraphics{figures/measures_richness.png}
\caption{Structure of empirical and maximum entropy food webs (type II
MaxEnt network model) as a function of species richness. Empirical
networks include all food webs archived on Mangal, as well as the New
Zealand and Tuesday lake datasets (our complete dataset). Maximum
entropy networks were derived using a simulating annealing algorithm to
find the network of maximum SVD entropy while maintaining the joint
degree sequence. (a) Nestedness (estimated with the spectral radius of
the adjacency matrix), (b) the maximum trophic level, (c) the network
diameter (i.e., the longest shortest path between all species pairs),
and (d) the SVD entropy were measured on these empirical and predicted
food webs and plotted against species richness. Regression lines are
plotted in each panel.}\label{fig:measures_richness}
}
\end{figure}

>>>>

\begin{figure}
\hypertarget{fig:kin_kout_diff}{%
\centering
\includegraphics{figures/kin_kout_difference.png}
\caption{Difference between predicted and empirical values for the
relative number of predators \(k_{in}\) and the relative number of prey
\(k_{out}\) when species are ordered according to (a) their out-degree
and (b) their in-degree. Empirical networks include most food webs
archived on Mangal, as well as the New Zealand and Tuesday lake datasets
(our complete dataset). The predicted joint degree sequences were
obtained after sampling one realization of the joint degree distribution
of maximum entropy for each network, while keeping the total number of
interactions constant. In each panel, each dot corresponds to a single
species in one of the networks.}\label{fig:kin_kout_diff}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:entropy_dist}{%
\centering
\includegraphics{figures/entropy_distribution.png}
\caption{(a) Distribution of the SVD entropy of MaxEnt food webs (type
II MaxEnt network model) and of empirical food webs. Empirical networks
include most food webs archived on Mangal, as well as the New Zealand
and Tuesday lake datasets (our complete dataset). Maximum entropy
networks were derived using a simulating annealing algorithm to find the
network of maximum SVD entropy while maintaining the joint degree
sequence. (b) Distribution of z-scores of the SVD entropy of all
empirical food webs. Z-scores were computed using the mean and standard
deviation of the distribution of SVD entropy of MaxEnt food webs (type
II MaxEnt network model). The dash line corresponds to the median
z-score.}\label{fig:entropy_dist}
}
\end{figure}

\begin{figure}
\hypertarget{fig:entropy_size}{%
\centering
\includegraphics{figures/difference_entropy.png}
\caption{Difference in SVD entropy between MaxEnt (type II MaxEnt
network model) and empirical food webs as a function of (a) species
richness, (b) the number of links, and (c) connectance. Empirical
networks include most food webs archived on Mangal, as well as the New
Zealand and Tuesday lake datasets (our complete dataset). Maximum
entropy networks were derived using a simulating annealing algorithm to
find the network of maximum SVD entropy while maintaining the joint
degree sequence. Regression lines are plotted in each
panel.}\label{fig:entropy_size}
}
\end{figure}

\begin{figure}
\hypertarget{fig:measures_richness}{%
\centering
\includegraphics{figures/measures_richness.png}
\caption{Structure of empirical and maximum entropy food webs (type II
MaxEnt network model) as a function of species richness. Empirical
networks include most food webs archived on Mangal, as well as the New
Zealand and Tuesday lake datasets (our complete dataset). Maximum
entropy networks were derived using a simulating annealing algorithm to
find the network of maximum SVD entropy while maintaining the joint
degree sequence. (a) Nestedness (estimated with the spectral radius of
the adjacency matrix), (b) the maximum trophic level, (c) the network
diameter (i.e., the longest shortest path between all species pairs),
and (d) the SVD entropy were measured on these empirical and predicted
food webs and plotted against species richness. Regression lines are
plotted in each panel.}\label{fig:measures_richness}
}
\end{figure}
